---
title: "Data Post Processing"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, message=FALSE, warning=FALSE}
library(data.table)
library(readxl)
library(dplyr)
library(lubridate)
```

# Data post processing
This notebook introduces the post processing plan for our analysis. 
1. reading data
2. merging data
3. feature engineering
(a) possible spillover
(b) message language
(c) upcoming reminder message date
4. saving processed data file

## Read data
1. assigned - assignment to treatment and control - this data contains all of the units and covariates as they were assigned to treatment and control.
2. covariates - account data - raw data from REDACTED that contains a variety of meta data
3. accounts_potential_spillover - spillover units - these are units that share a lat and long per analysis
4. message log
```{r read data}
assigned <- fread("../data/processed/assignment_to_treatment_and_control.csv")

covariates <- fread("../data/raw/20220608_accounts.csv")

covariates <- covariates[ , c('account_number','group_name','unlock_price',
             'responsible_user','customer_gender','customer_age',
             'customer_region','customer_occupation')]

accounts_potential_spillover <- fread("../data/processed/accounts_with_shared_lat_long.csv")

# extract accounts that have spillover to a vector
accounts_potential_spillover <- accounts_potential_spillover[ , account_number]

message_log <- fread("../data/processed/late_messages - Sheet1.csv")
```

```{r merge data}
accounts <- merge(assigned[eligible_for_exp == 1, ], covariates, by = 'account_number')
```

```{r some light cleaning}
# old index column that can be removed
accounts[ , V1 := NULL]

# re index alphabetic component
accounts[ , avg_days_past_due_group := case_when(
  avg_days_past_due_group == '(C) 1-7 days' ~ '(A) 1-7 days',
  avg_days_past_due_group == '(D) 8-29 days' ~ '(B) 8-29 days',
  avg_days_past_due_group == '(E) 30-59 days' ~ '(C) 30-59 days')]
```

```{r missing data}
# create dummy variable for missing age
accounts[ , missing_age := ifelse(is.na(customer_age), 1, 0)]

# set missing age value to 0
accounts[is.na(customer_age), customer_age := 0]

# create dummy variable for missing occupation
accounts[ , missing_occupation := ifelse(customer_occupation == "", 1, 0)]
```

## Feature engineering
### Possible spillover
```{r possible spillover}
# create dummy variable if account / subject possibly exposed to spillover
accounts[ , possible_spillover := (account_number %in% accounts_potential_spillover) * 1]

accounts[ , table(possible_spillover)]
```

### Message language
The message language is determined by the product purchased. Any unit with that has purchased the REDACTED product is sent a message in English. This is an expensive product and REDACTED assumes that anyone who purchases this product is wealthy, educated, and speaks English. If the unit is in the group REDACTED we denote the field "message_is_english" with a 1. 
```{r message language}
# create dummy if message sent is in English
accounts[ , message_is_english := grepl("REDACTED", group_name) * 1]

accounts[ , table(message_is_english)]
```

### Message timing
```{r generate table of account numbers and date of upcoming payment reminder}
upcoming_reminder_log <- data.table()

path_name = "../data/message_jobs/"

# vector of all upcoming payment reminder files
upcoming_payment_reminder_files <- list.files(path = path_name, pattern = 'upcoming')

start_date <- as.Date("20220617", format = "%Y%m%d")
end_date <- as.Date("20220717", format = "%Y%m%d")

for (i in 1:length(upcoming_payment_reminder_files)) {
  file_path <- paste(path_name, upcoming_payment_reminder_files[i], sep = "")
  
  date <- as.Date(substr(upcoming_payment_reminder_files[i], 1, 8), format = "%Y%m%d")
  
  # only aggregate accounts with message dates within experiment timeframe
  if (date >= start_date & date <= end_date) {
    temp_d <- data.table(read_excel(file_path))
    
    setnames(x = temp_d, old = "Account Number", new = "account_number")
    
    temp_d[ , account_number := as.integer(gsub(pattern = "'", replacement = "", x = account_number))]
    temp_d[ , upcoming_payment_reminder_date := date]
    
    upcoming_reminder_log <- rbind(upcoming_reminder_log, temp_d)
  }
}
```

```{r generate if account received multiple upcoming payment reminders}
upcoming_payment_reminder_counts <- data.table(
  upcoming_reminder_log %>%
    group_by(account_number) %>%
      tally(sort = TRUE))

setnames(x = upcoming_payment_reminder_counts, old = "n", new = "number_upcoming_messages")

accounts <- merge(x = accounts, y = upcoming_payment_reminder_counts,
                  by = 'account_number', all.x = TRUE)

accounts[is.na(number_upcoming_messages), number_upcoming_messages := 0]

# create dummy if account has received multiple upcoming messages
accounts[ , multiple_upcoming_messages_in_exp := (number_upcoming_messages > 1) * 1]

accounts[ , table(treat, multiple_upcoming_messages_in_exp)]
```

```{r generate if account has been administered experiment through message}
accounts[ , administered := (number_upcoming_messages > 0) * 1]

accounts[ , table(treat, administered)]
```

```{r generate day of week of first upcoming payment reminder}
first_upcoming_date_by_account <-
  upcoming_reminder_log[ , .(first_upcoming_date = min(upcoming_payment_reminder_date)),
           by = account_number]

first_upcoming_date_by_account[ , first_upcoming_char_date := wday(first_upcoming_date,
                                                                   label = TRUE)]

accounts <- merge(x = accounts, y = first_upcoming_date_by_account,
                  by = 'account_number', all.x = TRUE)

accounts[ , table(treat, first_upcoming_char_date)]
```

```{r clean message log table to see if messages delivered late in CAT}
# convert schedule date to proper format and then create column for CAT
message_log[ , datetime_sched_pt := paste(gsub(pattern = "/", replacement = "-",
                                         x = datetime_sched_pt))]
message_log[ , datetime_sched_pt := as.POSIXct(datetime_sched_pt,
                                               format = "%m-%d-%Y %T")]
message_log[ , datetime_sched_cat := datetime_sched_pt + hours(9)]

# convert delivery date to proper format and then create column for CAT
message_log[ , datetime_deliver_pt := paste(gsub(pattern = "/", replacement = "-",
                                         x = datetime_deliver_pt))]
message_log[ , datetime_deliver_pt := as.POSIXct(datetime_deliver_pt,
                                               format = "%m-%d-%Y %T")]
message_log[ , datetime_deliver_cat := datetime_deliver_pt + hours(9)]

# reduce columns to key ones
message_log <- message_log[ , c("date_sched","datetime_sched_cat",
                                "datetime_deliver_cat")]

message_log[ , delivered_late := ifelse(as.Date(datetime_sched_cat) == as.Date(datetime_deliver_cat), 0, 1)]
```

```{r generate if first upcoming message reminder late or not}
# static vector of days when scheduled messages delivered late
late_days <- message_log[delivered_late == 1, date_sched]

accounts[ , first_upcoming_message_late := ifelse(first_upcoming_date %in% late_days, 1, 0)]

accounts[ , table(treat, first_upcoming_message_late)]
```

```{r generate if any upcoming message reminder late or not}
accounts_with_any_late_message <- 
  upcoming_reminder_log[upcoming_payment_reminder_date %in% late_days, account_number]

accounts[ , any_upcoming_message_late := ifelse(account_number %in% accounts_with_any_late_message, 1, 0)]

accounts[ , table(treat, any_upcoming_message_late)]
```

```{r create static file to use}
write.csv(x = accounts,
          file = "../data/processed/accounts_with_post_processing.csv",
          row.names = FALSE)
```

